Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2021-12-22 article.rnw
some DBS edits to and comments about the article up to the Discussion

@@

@@

Models have long been used in community ecology \parencite{lotka1925elements}.
They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing}, or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide.

However, making any use of a model requires experimentally or observationally determining the values of each parameter in the model.
This poses a problem for species interaction models, due to the sheer number of parameters that must be determined.
Even the simplest models, with no environmental dependence, require one parameter for the interaction of each pair of species \parencite{novak2016characterizing}.
Hence the number of parameters scales quadratically with the number of species; over \num{100} parameters are required for a community of just \num{10} species.
Determining these parameters experimentally requires at least one experiment per parameter, and preferably more \parencite{hart2018quantify}.
This is expensive, and requires a lot of effort.
As such, these models are typically restricted to a small number of focal species \parencite{ovaskainen2017species}.
Real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
We need a way to reduce the number of parameters the models require, to regularise them.

@@

Regularisation is often performed by assuming that species fall into groups, such that all species in the same group interact with other species in the same fashion, thereby collapsing interaction parameters for all the species in that group into one parameter \parencite{ovaskainen2017species,weiss2021disentangling}.
Such groups have been defined \emph{a priori}, by phylogeny at some taxonomic level, or by functional groupings \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
The argument for grouping based on phylogeny is based on the principle (originally hypothesised by Darwin himself) that closely related species will be similar in (what we now know as) ecological niche, and thereby will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
However, tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant}.
While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
As such, applying these to species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
In all, we are left with the question of how best to group species in community models.

I propose that groups might be selected without regard to any \emph{a priori} definition, based purely upon which grouping gives the most parsimonious model.
In this study, I investigate the usefulness and correctness of such a selection, using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
I fit the Lotka--Volterra model, with grouped species, to find the grouping that gives the most parsimonious model.
I group species independently with regard to their effects upon other species and their responses to other species, to find whether the appropriate groupings might differ for these two cases.
Finally, I compare the resultant groupings with species phylogeny, to provide further investigation of the suitability of \emph{a priori} phylogenetic grouping.

@@

The data I used in this study were drawn from the work of \textcite{terry2021natural}.
The data consist of fecundity measurements---number of surviving offspring---for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
In this, they form essentially the standard experimental design for parameterising a species interaction model, as described by \textcite{hart2018quantify}.

@@

The experiment used six species of \emph{Drosophila} from an Australian rainforest community: \emph{D. birchii}, \emph{D. pallidifrons}, \emph{D. pandora}, \emph{D. pseudoananassae}, \emph{D. simulans}, and \emph{D. sulfurigaster}.
The experiment took place in vials with a limited amount of medium for egg-laying and larval development; competition was for space on this medium.
A number of adult pairs of one or two species were added to each vial and allowed to mate and lay eggs.
The number of adult pairs of each species emerging from these eggs---i.e.\ the size of the next generation---was the response variable.

@@

The experiment also included a number of other vials that were excluded from the analysis for various reasons.
The original authors' study was on parasitism, so the experiments also included a parasitised treatment.
That is irrelevant to this study, so was excluded.
Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra model cannot accommodate.
Lastly, an additional set of vials were raised in colder temperatures, but were excluded from this study and the original authors' as the resulting emergence was too low to analyse.

@@

I fitted the Lotka--Volterra competition model to the data.
As the response variable was fecundity, I used a discrete-time version of the model, as follows:
\[
	N_{i,t+1} = N_{i,t} r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
,\]
where $N_{i,t}$ is the population of species $i$ at time $t$, $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the \emph{per capita} competitive effect of species $j$ upon species $i$.
$N_{i,t+1}$ is the size of the population in the following time-step, i.e.\ the number of surviving offspring, the fecundity, of the previous generation, and therefore is equal to the experimentally measured response variable.
The competition coefficients were not constrained to be positive, allowing for the possibility of mutualistic effects between some species.

@@

The competition coefficients of the Lotka--Volterra model are typically arranged in an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects upon a single species, and a column contains all the competitive effects produced by a single species.
This interpretation was used in the grouping of species, as it was rows or columns of this matrix that were grouped.

Grouping was performed by constraining appropriate competition coefficients to be equal, reducing the number of free parameters in the model.
Each model fit was performed with one grouping of the interaction matrix's rows, and an independent grouping of the columns.
A grouping, known as a partition in mathematics, divides the species into groups such that each species belongs to one and only one group, and such that every group contains at least one species.
Given $n$ species, there may be any integer number of groups from $1$ to $n$.
With $n$ groups, the grouping places each species into its own group, as though there were no grouping at all.
With $1$ group, every species is placed in the same group, such that all are considered to be equal in their competitive effect or response, reminiscent of the neutral model.
Intermediate numbers of groups give more freedom in the groupings, such that there are many possible groupings for any intermediate number of groups.
The total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
With six species, and the row and column groupings chosen independently, the total number of possible models is $B_6^2 = \num{\Sexpr{numbers::bell(6)^2}}$.

Species in the same column grouping were constrained to have the same competitive effect upon all other species, while species in the same row grouping were constrained to have the same competitive response to all other species.
Formally, if species $a$ and $b$ were in the same column grouping, $\alpha_{ia}=\alpha_{ib} \, \forall i$, and if $a$ and $b$ were in the same row grouping, $\alpha_{aj}=\alpha_{bj} \, \forall j$.
As such, the total number of free competition coefficients in the model was equal to the number of row groups multiplied by the number of column groups.
The species' intrinsic growth rates, $r_i$, were not affected by grouping; each species always had its own growth rate fitted independently of other species.

@@

The models were fitted to the data using maximum likelihood regression techniques.
Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
As such, I assumed a normal error distribution, and fitted a least squares regression.
To prevent heteroskedasticity, I used the \emph{per capita} fecundity as the response variable, as in the following model:
\[
	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
.\]

The Lotka--Volterra model is not linear in the parameters.
With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters, by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$.
With the rows grouped, however, this becomes impossible, for each species still has its own growth rate.
As such, the models were fitted by the Gauss--Newton method for non-linear least squares.

@@

To assess the parsimony of each model, all \num{\Sexpr{numbers::bell(6)^2}} possible models were fitted.
As a measure of parsimony, I selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' model \parencite{aho2014model}.
Further, AIC is more conservative in promoting grouping, as BIC penalises number of parameters more for any reasonably sized data set.
As such, I calculated the AIC for each model.

AIC values can be compared to determine which is the most parsimonious model, but cannot directly be interpreted to find the significance of the difference in parsimony.
As such, I converted the set of AIC values to Akaike weights \parencite{wagenmakers2004aic}.
These give the probability, for each model, that it is the best among the models assessed.
All tests were based upon the relationship between the groupings used in a model and the Akaike weight of the model.

@@

\subsection{Phylogeny}

@@

Considering only models in which the rows and columns were grouped using the same grouping, the AIC values ranged from \aicnum{\Sexpr{min(brute_data$equivalently_grouped_statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$equivalently_grouped_statistics$aic)}}; neither the best nor worst overall models had equivalently grouped rows and columns.
The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).

@@

The ``best'' model, as indicated by AIC, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics$aic_weight)}} that it was the best.
As such, I assessed the appropriate groupings by taking the total probability that whichever was the best model grouped a given pair of species together (i.e.\ coclassified the pair of species).
These results are shown in \cref{fig:coclassification}.

In all, no pair of species can confidently be said to be coclassified, in the row or column groupings; no probability of coclassification exceeded \SI{60}{\percent}.
Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.

The structure of the coclassifications was very different in the row groups than in the column groups.
Most pairs of species which had a high probability of being coclassified in one grouping had a very low probability of being coclassified in the other grouping.
Only one pair of species had a relatively high probability of being coclassified in both groupings: \emph{D. pallidifrons} and \emph{D. sulfurigaster}.
Overall, more coclassification occurred in the row groupings than in the column groupings.

>>>>

% DBS: We should have a conversation regarding authorship. To me, it makes perfect sense thus far that you are the sole author. Depending on how revisions go and what anyone else or I do or do not contribute, it may be appropriate for this to change. In many such instances, I often think that the lead author (i.e., you) will have the best feeling for this relative to the criteria set out in the Vancouver guidelines for authorship.

@@

% DBS: I'll leave the abstract free of comments until the main text is closer to the final version.

@@

Models have long been used in community ecology \parencite{lotka1925elements}.
They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing}, or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide \parencite{XXX}.

Making practical use of a model requires experimentally or observationally determining the values of each of the model's parameters.
This poses a particular problem for models that include species interactions due to the sheer number of parameters that must be determined.
Even the simplest models with no environmental dependence require one parameter to characterize the interaction of each pair of species \parencite{novak2016characterizing, XXX}.
Hence the number of parameters scales quadratically with the number of species; over \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.
Determining these parameters experimentally requires at least one experiment per parameter, and preferably more \parencite{hart2018quantify}.
This is expensive, and requires a lot of effort.
As such, model-based predictions of real communities are typically restricted to a small number of focal species \parencite{ovaskainen2017species, XXX}.
However, real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
To bridge this gap between XXX and YYY, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.

@@

In the statistical literature, regularisation is the process of using external information to prevent overfitting or to solve an otherwise overspecified problem \parencite{XXX}. One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{XXX}. XXX why this could be a problem XXX
Alternatively, one can assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.

In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional groupings \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
The argument for grouping based on phylogeny is based on the principle (originally hypothesised by Darwin himself \cite{XXX}) that closely related species will be similar in (what we now know as) ecological niche, and thereby will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
% DBS: the preceding sentence could be simplified a fair bit
However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant}.
While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
As such, integrating these into species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
In all, we are left with the question of how best to group species in community models, and whether we can do so in a meaningful fashion with less data than required for a fully pairwise parameterisation.

I propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
% DBS: We can say something here about how this data-informed approach has worked very well for other clustering problems, such as modularity in networks. I can point to some very good references along those lines.
In this study, I investigate the usefulness and correctness of such an approach using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}. I fit the Lotka--Volterra model, with grouped species, to find the grouping that gives the most parsimonious model.
I group species independently with regard to their effects upon other species and their responses to other species, to find whether the appropriate groupings might differ for these two cases.
Finally, I compare the resultant groupings with species phylogeny, to provide further investigation of the suitability of \emph{a priori} phylogenetic grouping.
% DBS: I feel like the last sentences of this paragraph, from "In this study,..." onward should be rephrased to be more user friendly and without introducing new concepts (e.g., rows vs columns). If that info is important for the introduction, it ought to appear before the "This is what we do here" paragraph.

@@

The data I used in this study were drawn from the work of \textcite{terry2021natural}.
The data consist of fecundity measurements---number of surviving offspring---for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
This experimental design corresponds to a response--surface experimental design commonly used to parameterise a species interaction model \textcite{hart2018quantify, XXX}.

@@

The experiment used six species of \emph{Drosophila} from an Australian rainforest community: \emph{D. birchii}, \emph{D. pallidifrons}, \emph{D. pandora}, \emph{D. pseudoananassae}, \emph{D. simulans}, and \emph{D. sulfurigaster}.
The experiment took place in vials with a limited amount of medium for egg-laying and larval development; competition was for space on this medium.
A fixed number of adult pairs of one or two species were added to each vial and allowed to mate and lay eggs.
The number of adult pairs of each species emerging from these eggs---i.e.\ the size of the next generation---was the response variable.
% DBS: CRPB to fix this response variable when he fixes the model formula to reflect number of offspring.

@@

% DBS: We should probably remove all of the following except the bit about a single founding pair since it's the only thing with direct bearing on how this model gets fit. For reference, it's not hard to add an Allee effect to a LV model if we wanted to add another set of parameters, though I understand why we probably don't!
The experiment also included a number of other vials that were excluded from the analysis for various reasons.
The original authors' study was on parasitism, so the experiments also included a parasitised treatment.
That is irrelevant to this study, so was excluded.
Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra model cannot accommodate.
Lastly, an additional set of vials were raised in colder temperatures, but were excluded from this study and the original authors' as the resulting emergence was too low to analyse.

Further details of the experimental methodology can be found in \textcite{terry2021natural}.

@@

As the response variable was fecundity, I used a discrete-time version of the Lotka--Volterra competition model given by:
\[
	N_{i,t+1} = N_{i,t} r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
,\]
% DBS: CRPB to update the equation above after consideration of experimental response variable.
where $N_{i,t}$ is the population of species $i$ at time $t$, $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the \emph{per capita} competitive effect of species $j$ on species $i$.
$N_{i,t+1}$ is the size of the population in the following time-step, i.e.\ the number of surviving offspring, the fecundity, of the previous generation, and therefore is equal to the experimentally measured response variable.
The competition coefficients were not constrained to be positive, allowing for the possibility of mutualistic effects between some species.

% DBS: We might want to be prepared for reviewers asking us to change from a linear LV model.

@@

The set of competition coefficients in the Lotka--Volterra model can be  arranged in an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
This interpretation was used in the grouping of species, as it was rows or columns of this matrix that were grouped.
% DBS: Similar to my comment above, I'm not sure the rows vs column groupings is sufficiently introduced to this point. So I think we need more than a single sentence explaining this idea. Since it appears below, we can reiterate the meaning in terms of equivalence of competitive responses and equivalence of competitive effects.

Grouping was performed by constraining appropriate competition coefficients to be equal, reducing the number of free parameters in the model.
Each model fit was performed with one grouping of the interaction matrix's rows and a second, independent grouping of the matrix's columns.
A grouping, known as a partition in mathematics, divides the species into groups such that each species belongs to one and only one group, and such that every group contains at least one species.
Given $n$ species, there may be any integer number of groups from $1$ to $n$.
With $n$ groups, the grouping places each species into its own group, such that all species interact in a unique fashion.
With $1$ group, every species is placed in the same group, such that all are equal in their competitive effects or responses, reminiscent of the neutral model.
Intermediate numbers of groups give more freedom in the groupings, such that there are many possible groupings for any intermediate number of groups. % DBS: Is this sentence essential?
The total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
With six species and independently selected row and column groupings, the total number of possible models is ${\left(B_6\right)}^2 = \num{\Sexpr{numbers::bell(6)^2}}$.

Species in the same column grouping were constrained to have the same competitive effect upon all other species, while species in the same row grouping were constrained to have the same competitive response to all other species.
Formally, if species $a$ and $b$ were in the same column grouping, $\alpha_{ia}\equiv\alpha_{ib} \, \forall i$, and if $a$ and $b$ were in the same row grouping, $\alpha_{aj}\equiv\alpha_{bj} \, \forall j$.
As such, the total number of free competition coefficients in the model was equal to the number of row groups multiplied by the number of column groups.
The species' intrinsic growth rates, $r_i$, were not affected by grouping; each species always had its own growth rate fitted independently of other species.

% DBS: I think my comments at the top of the previous section really boil down to simply reorganizing the pieces in the different paragraphs so that they more clearly build on each other linearly.

@@

The Lotka--Volterra model is not linear in the parameters.
With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$ pair.
With the rows grouped, however, this becomes impossible since each species still has an independent growth rate.
As such, the models were fitted by the Gauss--Newton method for non-linear least squares.
%The models were fitted to the data using maximum likelihood regression techniques.
%Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
I assumed a normal error distribution of the response variable. and 
to prevent heteroskedasticity and improve normality, I transformed total fecundity to \emph{per capita} fecundity, which corresponds to the following model:
\[
	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
.\]
% DBS: CRPB to alter equation above consist with changes to previous equations.

@@

To assess the parsimony of the different species groupings, I exhaustively fit all \num{\Sexpr{numbers::bell(6)^2}} possible models.
As a measure of parsimony, I selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' model \parencite{aho2014model}.
Further, AIC is more conservative in promoting grouping, as BIC penalises number of parameters more for any reasonably sized data set.
As such, I calculated the AIC for each model.
% DBS: Is it possible that the dataset is small enough that we should be using AICc instead?

AIC values can be compared to determine which model is the most parsimonious, but cannot directly be interpreted to find the significance of the difference in parsimony.
As such, I also converted the set of AIC values to Akaike weights \parencite{wagenmakers2004aic}.
These give the probability that each model is the best among the models assessed.
All tests were based upon the relationship between the groupings used in a model and the Akaike weight of the model.
% DBS: I find the last sentence above to be worded a bit cryptically.

@@

\subsection{Phylogeny}
% DBS: For now, I would cut out the bit about phylogeny since it's relatively weak without a properly calibrated tree. If you want to do a post hoc test, I would go with one that looks at body size and co-classification matrices. On the other hand, my gut tells me that the paper stands on its own merits without a post hoc test, and this is an easy thing to guide reviewers toward commenting on/requesting that you also know how to address. So it might be a useful strategic omission.

@@

Considering only models in which the rows and columns were grouped using the same grouping, the AIC values ranged from \aicnum{\Sexpr{min(brute_data$equivalently_grouped_statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$equivalently_grouped_statistics$aic)}}; neither the best nor worst overall models had equivalently grouped rows and columns.
The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
% DBS: I think the last sentence above needs a bit of elaboration here OR the usefulness of this "test" should be explained in the Methods in the section that discusses how we examined aspects of parsimony.

@@

The ``best'' model, as indicated by AIC, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics$aic_weight)}} that it was the best.
As such, I assessed the appropriate groupings by taking the total probability that whichever was the best model grouped a given pair of species together (i.e.\ coclassified the pair of species).
These results are shown in \cref{fig:coclassification}.
% DBS: Much of the paragraph above is probably more appropriate at Methods text whereas in the Results we should discuss the patterns that emerge from the co-classification matrices.

In all, no pair of species can confidently be said to be coclassified, in the row or column groupings; no probability of coclassification exceeded \SI{60}{\percent}.
Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.
% DBS: As I have noted before, I'd like to know what the null expectation is for this before claiming confidence of being co-classified or not being co-classified. Firstly, I think that the random expectation is much lower than one might otherwise suspect. (For three species, it is already 2/5.) Second, the conventional "ecological" null is actually that the probability is 0, in which case it doesn't take much co-classification probability to see the glass as half full and argue that grouping is a much more parsimonious approach than the contrary.

The structure of the coclassifications was very different in the row groups than in the column groups.
Most pairs of species which had a high probability of being coclassified in one grouping had a very low probability of being coclassified in the other grouping.
Only one pair of species had a relatively high probability of being coclassified in both groupings: \emph{D. pallidifrons} and \emph{D. sulfurigaster}.
Overall, more coclassification occurred in the row groupings than in the column groupings.
% DBS: In the network modularity literature, there is a nice measure of mutual information between two partitions. I wonder if we could exploit that here to give a quantitative measure of similarity between the two. Or we could just convert the two matrices to distance matrices and run a Procrustes to measure their similarity?
